MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-11-14 article/main.tex
Proof for theft prevention added

\subsubsection{Theft prevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:

@@

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$. This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers. 
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they broke discrete logarithm problem on the secp256k1 curve.
\begin{table}[H] 
	\caption{Security properties achieved by each coin mixing protocol.}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}

@@

\section{Proof of Anonymity}
Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.

@@

\section{Proof of Availability}
\section{Proof of Theft Prevention}

>>>>

\subsubsection{Theft prevention} \label{sec:theftprevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:

@@

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$. This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability. See reduction proof in Appendix \ref*{appendanon}.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient. This contradicts to the assumption that ECDSA is existentially unforgeable. Reduction proof is enclosed in Appendix \ref*{appendtheft}. 
\begin{table}[H] 
	\caption{Security properties achieved by each coin mixing protocol.}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}

@@

\section{Proof of Anonymity} \label{appendanon}
Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.

@@

\section{Proof of Availability}  \label{appendavail}
\section{Proof of Theft Prevention} \label{appendtheft}

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\begin{bbrenv}{A}
		\begin{bbrbox} [name=\bdv]
			\pseudocode {
				\text{$(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]$} \\
				\text{$\textsf{PK}_{B}\leftarrow\{pk_{i}\}_{i=1}^{n}$;$C, H_{\omega}, contract \leftarrow \emptyset$}
			}

			\begin{bbrenv}{B}
				\begin{bbrbox}[name=\adv]
					\pseudocode{
						\text{Input: $(1^{\lambda},PK_{B})$} \\
						\text{$(tx,j) \stackrel{\$}{\leftarrow}\adv^{CORR,AD,AW,HW}(1^{\lambda},PK_{B})$} \\
						\text{Output: $(tx,j)$}
					}
				\end{bbrbox}

		\end{bbrbox}
		\bbrinput{$1^\lambda$}
		\bbroutput{$(tx,\sigma_{tx})$}
	\end{bbrenv}

	\captionof{figure}{An illustration for the reduction of theft prevention to the existentially unforgeability of ECDSA.}
\end{wrapfigure}

Towards contradiction we assume that there exists an adversary $\adv$, who is able to break the theft prevention property introduced in Section \ref{sec:theftprevention} with non-negligible probability. Using such an adversary as a subroutine we could create another efficient adversary $\bdv$ who is able to break the existential unforgeability of ECDSA. The input of the forgeability game is the security parameter which is forwarded to $\adv$ along with $n$ randomly generated public keys. By assumption $\adv$ outputs with non-negligible probability valid withdraw transaction belonging to one of the public keys in the mixer. $\bdv$ outputs the withdraw transaction and the ECDSA signature on it. $\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$. This contradicts to the assumption that ECDSA is existentially unforgeable.
